A* with Perfect Potentials

### 2020-04-11 paper/ch_potentials.tex
foo

\section{Avoid Placing Nodes in The Queue}

@@

\subsection{Largest Biconnected Component}

@@

\begin{itemize}
\item Avoid nothing running times, i.e., what is if $w_q = q_\ell$?
\item Multiply all weights by $\alpha$ for $\alpha$ in 1.1, 1.5, 2, 3
\item Avoid highway
\item Avoid tunnel
\item Avoid highway + tunnel
\item MapBox Live Traffic
\item Ptv-TD traffic? Achtung: Das Fass würde ich nicht aufmachen. Am Ende will ein Reviewer, dass wir avoid highway mit TD kombinieren... das ist NP-schwer
\item Running times if OSM degree 2 nodes are not extracted!
\end{itemize}

>>>>

\section{Avoiding Potential Function Evaluations}

@@

\subsection{Avoid Dead-Ends using Largest Biconnected Component}

@@

\begin{itemize}
\item Avoid nothing running times, i.e., what is if $w_q = w_\ell$?
\item Multiply all weights by $\alpha$, i.e., $w_q = \alpha w_\ell$ for $\alpha$ in 1.1, 1.5, 2, 3
\item Avoid highway
\item Avoid tunnel
\item Avoid highway + tunnel
\item MapBox Live Traffic
\item Ptv-TD traffic? Achtung: Das Fass würde ich nicht aufmachen. Am Ende will ein Reviewer, dass wir avoid highway mit TD kombinieren... das ist NP-schwer
\item Running times if OSM degree 2 nodes are not extracted! Das einzige Argument pro Erhalten von Deg 2 das ich bisher kenne ist MapBox Live Traffic matchen.
\end{itemize}
